\documentclass[a4paper, 11pt]{article} 

\usepackage[a4paper, margin=0.5in]{geometry} 

\usepackage{enumitem}



\begin{document}

\begin{center}
    {\Huge \textbf{Jawadul Islam (Salvin) Chowdhury}} \\
    \vspace{0.2cm}
    {\large Milwaukee, WI ~\textbullet~ chowdhuryjawadul@icloud.com ~\textbullet~ (414) 801-0784}
\end{center}

\section*{SUMMARY}
\vspace{-0.2cm}  
\hrule
\vspace{0.2cm}
B.S Computer Science student at the Milwaukee School of Engineering with hands-on experience in data cleaning,
visualization, statistical modeling and teams-based project experience in competitions. Devoting 4+ hours per week to
co-curriculars and have skills in Pandas, NumPy, SciPy, Matplotlib \& Scikit-learn.

\section*{EDUCATION}
\vspace{-0.2cm}  
\hrule
\vspace{0.2cm}
\textbf{Bachelor of Sciece in Computer Science} \(\mid\) Expected May 2027 \\
Milwaukee School of Engineering ~ \textbullet ~ Milwaukee, WI \\
\textbf{Cumulative GPA:} 3.3

\section*{TECHNICAL SKILLS}
\vspace{-0.2cm}  
\hrule
\vspace{0.2cm}
\textbf{Languages:} Python \& R \\
\textbf{Software \& Technologies:} GitHub, Jupyter Notebook, Anaconda \& Visual Studio Code \\
\textbf{Skills:} Pandas, NumPy, SciPy, Matplotlib, Scikit-learn, Tensorflow, Seaborn, Pytorch \& Plotly

\section*{DATA SCIENCE EXPERIENCE}
\vspace{-0.2cm}  
\hrule
\vspace{0.2cm}
\textbf{Company Bankruptcy Prediction} \hfill \textbf{December 2024} \\
\textbf{Objective:} Using a set of machine learning models used to predict a company's likelihood
of bankruptcy
\vspace{-0.2cm}
\begin{itemize}[left=0pt]
    \setlength{\itemsep}{-0.2em}
    \item Applied min-max normalization for data pre-processing to maintain relationships between data points.
    \item Developed K-Means clustering and evaluated performance using Silhouette Score for cluster cohesion.
    \item Tuning hyperparameters by experimenting with clusters, activation functions, neurons \& dropout layers.
\end{itemize}

\section*{RESEARCH EXPERIENCE}
\vspace{-0.2cm}  
\hrule
\vspace{0.2cm}
\textbf{Undergraduate Research Assistant} \hfill \textbf{January 2024 - Present}
\vspace{-0.2cm}
\begin{itemize}[left=0pt]
    \setlength{\itemsep}{-0.2em}
    \item Collaborating with Dr.Kedziora on a project focusing on sequential model-based optimization.
    \item Developing parallelized processing techniques for reinforcement learning algorithms using the ray library.
    \item Performing statistical analysis to evaluate performance of models using bayesian additive regression trees.
\end{itemize}

\section*{EXTRACURRICULAR EXPERIENCE}
\vspace{-0.2cm}  
\hrule
\vspace{0.2cm}
\textbf{MKE TECH FUSE Bootcamp} \hfill \textbf{June 2024 - August 2024}
\vspace{-0.2cm}
\begin{itemize}[left=0pt]
    \setlength{\itemsep}{-0.2em}
    \item Awarded a fully-funded scholarship from the MKE TECH Hub to participate in the bootcamp program.
    \item Collaborated in a team of 5 students to develop an extension helping betters to win bets frequently.
    \item Achieved “In it to win it” award \& Higher Education Regional Alliance (HERA) technology badge.
\end{itemize}

\textbf{UW Madison MadHacks} \hfill \textbf{November 2024}
\vspace{-0.2cm}
\begin{itemize}[left=0pt]
    \setlength{\itemsep}{-0.2em}
    \item Awarded a fully-funded scholarship from the MKE TECH Hub to participate in the bootcamp program.
    \item Collaborated in a team of 5 students to develop an extension helping betters to win bets frequently.
    \item Achieved “In it to win it” award \& Higher Education Regional Alliance (HERA) technology badge.
\end{itemize}

\end{document}
